---
title: "2026 IT Prof Conf Data Report"
author: "Spencer Bailey"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
```


```{r, include = FALSE}
# Library Loads...
library(readxl)
library(dplyr)
library(ggplot2)
library(stringr)
library(tidyverse)
library(grDevices)
library(knitr)
library(kableExtra)
library(lubridate)

```

___
### [Conference Registration and Attendance Metrics]{.underline}


```{r}

# Data Load:

# 1. Read Excel Data
ohrd_registration <- read_excel(
  "./2026 Registrations.xlsx", 
  .name_repair = function(col)
    { 
      gsub(" ", "_", col) 
    }
)

zoom_registration <- read_excel(
  "./Zoom Registrations 2026.xlsx", 
  .name_repair = function(col)
    { 
      gsub(" ", "_", col) 
    }
) %>%
  add_count(Email, name = "email_count") %>%
  # 2. Filter out rows that meet ALL your conditions:
  #    Missing names AND the email appears more than once, keep original
  filter(!(First_name == "N/A" & Last_name == "N/A" & email_count > 1)) %>%
  # 3. Drop the temporary counter column
  select(-email_count) %>%
  filter(!Email %in% c("kozitzky@wisc.edu", "skhan@perscholas.org", "steffes@ortho.wisc.edu", "cmdavis32@wisc.edu", "ddalsore@wisc.edu", "grash@wisc.edu", "jgvaldez@wisc.edu", "joschroeder@wisc.edu", "ngonzales@wisc.edu")) %>%
  filter(Ticket_type == "All Virtual") %>%
  mutate(Email = str_trim(tolower(Email))) %>%
  
  anti_join(
    ohrd_registration %>%
      mutate(Email = str_trim(tolower(Email))),
    by = "Email"
  ) %>%
  filter(Registration_method != "Host pre-registration")

reg_2017_to_2025 <- read_excel(
  "./Registrations_2017_to_2025.xlsx"
)

session_summary <- read_excel(
  "./Session_Summary_26.xlsx",
  .name_repair = function(col)
    { 
      gsub(" ", "_", col) 
    }
) %>%
  rename(Total_Attendees = `Total_Attendees_(including_views_during_the_conference)`)

# Rename ugly col name
zoom_registration <- zoom_registration %>% 
  rename(Registration_Date = `Last_registration_time`) %>%
  rename(Division = `What_is_your_school,_college,_or_division?_(do_not_abbreviate)_-_All_Virtual`) %>%
  rename(Title = `Job_title`)

```

#### Daily Registration Counts:

These first two charts represent registration of all attendees over the registration period, highlighting dates of targeted marketing efforts (CIO Office Hour Announcements, Campus Newsletter Announcements, InsideUW Ads, etc…). The first chart represents our registration punctuated by marketing efforts made through various campus newsletters. The second chart depicts our registrations punctuated by all remaining outreach efforts labeled descriptively. The goal in analyzing this data is to aid in strategically leveraging communication channels for the greatest outreach in future conference iterations. 

```{r}
# Initial Data Prep Chunk for registration data.

# Format Date to specification
ohrd_registration$Registration_Date <- as.Date(ohrd_registration$Registration_Date, format = "%Y-%m-%d")

zoom_registration$Registration_Date <- as.Date(
  zoom_registration$Registration_Date, 
  format = "%a, %b %d, %Y"
)

# Create the counts for OHRD Registrations
daily_reg_counts_ohrd <- ohrd_registration %>%
  group_by(Registration_Date) %>%
  count()

# Create the counts for zoom registrations
# Filter Out duplicates from OHRD.
# There were maybe like 3 duplicates that I did not get to filter out because of inconsistent emails used.
# Email is, unfortunately, the best key. Names are a bad key to use. Don't use names.
daily_reg_counts_zoom <- zoom_registration %>%
  group_by(Registration_Date) %>%
  count() %>%
  na.omit()

# Add col to each dataset to identify virtual or hybrid
# This will be important to distiguish hybrid from virtual registrations when merged.
daily_reg_counts_ohrd$Experience <- 'HYBRID'
daily_reg_counts_zoom$Experience <- 'VIRTUAL'

# Join the two registration tables together
daily_reg_counts <- rbind(daily_reg_counts_ohrd, daily_reg_counts_zoom)

```


```{r}
# Section to create Chart punctuated by newsletter outreach efforts specifically

# This will come from the Comms team.
newsletter_labels <- c(
  "2026-05-20" = "TechNews fac/staff",
  "2026-05-13" = "Working@UW",
  "2026-05-12" = "DoIT Connection & Inside UW Paid Ad",
  "2026-05-07" = "SMPH 'In the Know'",
  "2026-04-30" = "DoIT Connection",
  "2026-05-07" = "DoIT Connection",
  "2026-05-14" = "DoIT Connection",
  "2026-05-21" = "DoIT Connection"
)

ggplot(daily_reg_counts, aes(x=Registration_Date, y=n, fill=Experience)) +
  geom_bar(stat = "identity", position = "stack") +
  #this part is getting the list of all the dates and scaling that by that, but removing weekends
  scale_x_date(
    breaks = function(x) {
      weekday_dates <- seq(min(x), max(x), by = "1 day")
      weekday_dates[!weekdays(weekday_dates) %in% c("Saturday", "Sunday")]
    },
    labels = function(x) {
      # Format all dates over registration period as "dd/mm"
      formatted <- format(x, "%m/%d")
      
      # Replace labels for the event dates with the newsletter outreach labels
      event_dates <- as.Date(names(newsletter_labels))
      match_idx <- match(x, event_dates)
      
      formatted[!is.na(match_idx)] <- newsletter_labels[na.omit(match_idx)]
      formatted
    }
  ) +
  #using uw madison branding colors.
  scale_fill_manual(
    values = c(
      "VIRTUAL" = "#0479A8",
      "HYBRID" = "#9B0000"
    )
  ) +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)  # Rotate labels
  ) +
  xlab("Full Registration Period") +
  ylab("Daily Registration Tallys") +
  ggtitle("Newsletter Outreach Marketing Efforts")

```

From these two charts, it appears that the most successful marketing efforts to garner sign-ups is through our emails to listserves.

```{r}
# Chart punctuated by all other outreach efforts
# Everthing is the same here as above.

emails_and_ads_labels <- c(
  "2026-04-23" = "Email listserv/CoP",
  "2026-05-01" = "Email listserv/CoP",
  "2026-05-07" = "Email listserv/CoP",
  "2026-05-14" = "Email listserv/CoP",
  "2026-05-21" = "Email listserv/CoP",
  
  
  "2026-05-05" = "Inside UW Paid Ad",
  "2026-05-12" = "Inside UW Paid Ad"
  
)

ggplot(daily_reg_counts, aes(x=Registration_Date, y=n, fill=Experience)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_x_date(
    breaks = function(x) {
      weekday_dates <- seq(min(x), max(x), by = "1 day")
      weekday_dates[!weekdays(weekday_dates) %in% c("Saturday", "Sunday")]
    },
    labels = function(x) {
      # Format all dates as "dd/mm"
      formatted <- format(x, "%m/%d")
      
      # Replace labels for the event dates
      event_dates <- as.Date(names(emails_and_ads_labels))
      match_idx <- match(x, event_dates)
      
      formatted[!is.na(match_idx)] <- emails_and_ads_labels[na.omit(match_idx)]
      formatted
    }
  ) +
  scale_fill_manual(
    values = c(
      "VIRTUAL" = "#0479A8",
      "HYBRID" = "#9B0000"
    )
  ) +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)  # Rotate labels
  ) +
  xlab("Full Registration Period") +
  ylab("Daily Registration Tallys") +
  ggtitle("Emails to listserv/CoPs, InsideUW Ads, CIO Office Hours")

```

From these two charts, it appears that the most successful marketing efforts to garner registrations is through our emails to listserv. The second graph shows that that emails sent to our listserves coincided with weekly registration highs.

#### Demographic counts for registrants:

These next two charts represent demographic information about conference registrants. The first two charts break down registrants by their School/College/Division. The second two charts breaks registrants down by their position titles - which isn't complete as manually mapping all titles poses a big challenge and the data was subjected to some arbitrary groupings. The goal, however, in analyzing this demographic data in depth is to get a better sense of who our participants are, so that we might be able to, in future conference planning, identify what our primary participants might be most interested in to drive up our engagement.

```{r}

# Data Prep for demographic content 

# Create School/College/Division counts
scd_counts_ohrd <- ohrd_registration %>%
  mutate(Division = toupper(Division)) %>%
  mutate(Division = str_replace_all(Division, " AND ", " & ")) %>%
  group_by(Division) %>%
  count() %>%
  na.omit()

scd_counts_ohrd$Division <- sub(".*\\| ", "", scd_counts_ohrd$Division)

scd_counts_zoom <- zoom_registration %>%
  mutate(Division = toupper(Division)) %>%
  mutate(Division = str_replace_all(Division, " AND ", " & ")) %>%
  filter(Ticket_type == "All Virtual") %>%
  filter(!Email %in% ohrd_registration$Email) %>%
  group_by(Division) %>%
  count() %>%
  na.omit()

# Manual analysis of qualitative data entered manually that maps poorly...
# Zoom division info was entered manually in a form by registrants (sometimes it was there, sometimes people skipped the question), so I did some mapping myself here. It's not perfect, but is better than nothing. it might be better to do this in a new excel file this time and use a read for this.
#Reading excel file where I manually mapped items.

scd_counts_zoom_2 <- read_excel("./Zoom Workgroups.xlsx")

combined_scd <- bind_rows(scd_counts_ohrd, scd_counts_zoom_2) %>% 
  mutate(
    # 1. Force to character type to prevent Factor level splitting
    Division = as.character(Division),
    # 2. Strip leading/trailing/invisible spaces
    Division = str_squish(Division),
    # 3. Standardize casing to eliminate case mismatch
    Division = toupper(Division)
  ) %>% 
  group_by(Division) %>% 
  # 4. Handle any potential NA values that break grouping sums
  summarise(count = sum(as.numeric(n), na.rm = TRUE), .groups = "drop")

```

```{r}

# Data Prep section for Title Demographics.

#remove title numbering and parenthesis with regex
ohrd_registration$clean_title <- ohrd_registration$Title %>%
  str_remove("\\s*(\\([^()]*\\)\\s*){1,2}$") %>%    # Remove up to two instances of trailing (...) content
  str_remove("\\s+[IVXLCDM]+$") %>%                 # Remove trailing Roman numerals
  str_trim()

# Manual Title formatting changes, collapsing to consistent titles, removing incorrectly answered info
ohrd_registration <- ohrd_registration %>%
  mutate(clean_title = ifelse(clean_title == "STARTING 12/1/13- CALL 515-8399 TO REACH ME", NA, clean_title)) %>%
  mutate(clean_title = ifelse(clean_title == "TECH INT ENG", "TECHNICAL INTEGRATION ENG", clean_title)) %>%
  mutate(clean_title = ifelse(clean_title == "TEAM LEAD, IDENTITY AND ACCESS MANAGEMENT", "TEAM LEAD", clean_title)) %>%
  mutate(clean_title = ifelse(clean_title == "SOFTWARE ENG/DEVELOPER", "SOFTWARE ENGINEER/DEVELOPER", clean_title)) %>%
  mutate(clean_title = ifelse(clean_title == "IT PRO MGR", "IT MANAGER", clean_title)) %>%
  mutate(clean_title = ifelse(clean_title == "DIRECTOR", "IT DIRECTOR", clean_title)) %>%
  mutate(clean_title = ifelse(clean_title %in% c("BUSINESS ANALYSIS AND CHANGE MANAGEMENT ASSOCIATE DIRECTOR", "ASSOCIATE DIRECTOR, CAREER SERVICES", "ASSOCIATE DIRECTOR OF DESIGNLAB", "ASSISTANT DIRECTOR MERIT"), "ASSOCIATE DIRECTOR", clean_title))

# Create Counts
title_counts_ohrd <- ohrd_registration %>%
  group_by(clean_title) %>%
  count() %>%
  na.omit()

#remove title numbering and parenthesis with regex
zoom_registration$clean_title <- zoom_registration$Title %>%
  str_remove("\\s*(\\([^()]*\\)\\s*){1,2}$") %>%    # Remove up to two instances of trailing (...) content
  str_remove("\\s+[IVXLCDM]+$") %>%                 # Remove trailing Roman numerals
  str_trim()

title_counts_zoom <- zoom_registration %>%
  group_by(clean_title) %>%
  count() %>%
  na.omit()

# Manual analysis of title counts imported because data entered manually that maps poorly...


combined_title <- read_excel("./Compiled Titles.xlsx")


```

```{r}

#Lots of formatting stuff for this pie chart
pie_scd <- combined_scd %>%
  arrange(desc(count)) %>% #makes it go greatest to least
  mutate(
    Division_grouped = case_when(
      row_number() <= 10 ~ Division,  # keep top 10
      TRUE ~ "Other"
    ),
  ) %>% #mutate collapses everything beyond top 10 to an other category
  group_by(Division_grouped) %>%
  summarise(new_count = sum(count)) %>% #just joins all the 'other' items together
  mutate(percentage = new_count / sum(new_count)) %>%
  mutate(
    Division_grouped = paste0(
      "(", round(percentage * 100), "%", ") ", Division_grouped
    )
  ) %>% #add percentage to the labels
  mutate(
    Division_grouped = fct_reorder(Division_grouped, new_count, .fun = sum, .desc = TRUE),
    Division_grouped = fct_relevel(Division_grouped, "(19%) Other", after = Inf)
  )

#This creates different colors along a sort of color merge so that I could keep with branding
my_palette_11 <- colorRampPalette(c("#9B0000", "#333333", "#0479A8", "#F7F7F7"))(11)

ggplot(pie_scd, aes(x = "", y = new_count, fill = Division_grouped)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  theme_void() +  # removes axes and background
  labs(fill = "Division") +
  scale_fill_manual(values = my_palette_11)

```

```{r fig.height = 10, fig.width = 7.5}
# School/College/Division representation:

combined_scd$Division <- factor(combined_scd$Division, levels = combined_scd$Division[order(combined_scd$count)])

ggplot(combined_scd, aes(x = Division, y = count)) +
  geom_bar(stat = "identity", fill="#9B0000") +
  geom_text(
    data = combined_scd[combined_scd$count > 15, ],  # Only label bars exceeding the limit
    aes(label = count, y = 4),  # Pin label at top of visible area
    vjust = 0.4,
    angle = 0,         # Rotate text 90 degrees
    color = "#F7F7F7"
  ) +
  theme(
    # Rotate labels
    axis.text.y = element_text(angle = 0, hjust = 1, vjust = 0.5,)
  ) +
  xlab("Participant Work Organizations") +
  ylab("Registration Tallys") +
  ggtitle("Registration Tallys from Various Work Groups") +
  coord_flip(ylim = c(0, 80))
  

```


The key observation here is  our top 5 represented divisions. DoIT, SMPH, L&S, oVCFR and CALS comprised the greatest populations that registered for the conference this year. The top 5 follow with our findings during the 2025 IT Professionals Conference, and our top 3 follow with 2025 and 2024. 65% of our conference attendance is comprised of individuals from our top 5 units.

```{r}

pie_title <- combined_title %>%
  arrange(desc(n)) %>%
  mutate(
    Title_grouped = case_when(
      row_number() <= 10 ~ clean_title,  # keep top 10
      TRUE ~ "Other"
    ),
  ) %>%
  group_by(Title_grouped) %>%
  summarise(new_count = sum(n)) %>%
  mutate(percentage = new_count / sum(new_count)) %>%
  mutate(
    Title_grouped = paste0(
      "(", round(percentage * 100), "%", ") ", Title_grouped
    )
  ) %>%
  mutate(
    Title_grouped = fct_reorder(Title_grouped, new_count, .fun = sum, .desc = TRUE)
  )

my_palette_11 <- colorRampPalette(c("#9B0000", "#333333", "#0479A8", "#F7F7F7"))(11)

ggplot(pie_title, aes(x = "", y = new_count, fill = Title_grouped)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  theme_void() +  # removes axes and background
  labs(fill = "Title") +
  scale_fill_manual(values = my_palette_11)


```


```{r fig.height = 10, fig.width = 7.5}

combined_title$clean_title <- factor(combined_title$clean_title, levels = combined_title$clean_title[order(combined_title$n)])

# Position Title representation:
ggplot(combined_title, aes(x = clean_title, y = n)) +
  geom_bar(stat = "identity", fill="#9B0000") +
  geom_text(
    data = combined_title[combined_title$n > 18, ],  # Only label bars exceeding the limit
    aes(label = n, y = 1),
    vjust = 0.4,
    angle = 0,       # Rotate text 90 degrees
    color = "#F7F7F7",
    size = 3
  ) +
  theme(
    # Rotate labels
    axis.text.y = element_text(angle = 0, hjust = 1, vjust = 0.5,)
  ) +
  xlab("Participant Work Organizations") +
  ylab("Registration Tallys") +
  ggtitle("Registration Tallys from Various Position Titles") +
  theme(
    plot.title = element_text(hjust = 0)
  ) +
  coord_flip(ylim = c(0, 60))
  

```

This data is not quite as neatly compiled and is a bit more arbitrary based on how titles were grouped, but is worth looking into anyway. A key observation here is  our top 5 represented titles at the conference. The largest position group within the sample was Managers of various types. Though they make up a smaller proportion of our IT Professionals, they comprise a large proportion of our attendees. Our conference also attracted a good number of engineers and admins across various areas, General IT Professionals/Technicians/Support Persons, Developers, and Directors and Associate/Assistant Directors.

Although managers and directors make up a much smaller population of campus employees, together they represent the greatest proportion of conference attendees. Software Developers make up another large proportion of conference attendees, as do support persons. Increasing our breadth of content may be able to bring numbers up for smaller represented title groups.

#### Total attendee/registrant counts with comparison to previous year(s):

```{r}
# Manually create table for the yearly attendee/registrant counts with comparison to previous year(s)

data = matrix(c(9, 208, 217, 45, 230, 275, 36, 227, 263, NA, NA, 315, NA, NA, 286, 65, 396, 461, 74, 373, 447, 47, 486, 533, 48, 403, 451, 63, 469, 532), ncol=10)

rownames(data) <- c('Absent:', 'Attended:', 'Total:')
colnames(data) <- c('2017', '2018', '2019', '2020', '2021', '2022', '2023', '2024', '2025', '2026')

kable(as.data.frame(data))

```

```{r include = FALSE}

# Data Prep for bar chart, and export of the new excel file for use next year.

# Finding committee members & presenters with 'in kind' as their payment method
in_kind <- ohrd_registration %>%
  filter(Payment_Method == "In Kind")

all_reg_prep_zoom <- zoom_registration %>%
  mutate(
    COURSE_NAME = "IT Professionals Conference 2026",
    Attended = if_else(Participation == "Absent", 0, 1),
    NETID = sub("@.*", "", Email),
    PVI = NA,
    YEAR = "2026",
    `Dupplicate?` = 'No',
    `Ticket Type` = if_else(Email %in% in_kind$Email, "Special", "General")
  ) %>%
  select(COURSE_NAME, Attended, NETID, PVI, YEAR, `Dupplicate?`, `Ticket Type`)

live_absences = c("SCHILLER, KEITH R", "BAILEY, SPENCER C", "SULLIVAN, LILY M", "SCHOLZ, JASON R", "DIESTLER, AMY", "DIECKMAN, ERIC W", "NYLUND, BENJAMIN C", "ALAQIDY, RIVER A", "TINBERG, MARK", "SENGSTOCK, PETER G", "HANSON, LYLE D", "CZERWONKA, TIM", "MEADE, PATRICK M", "KUMARASIRI, NUWAN R", "KORPI, SARAH D", "JOHNSON, MANDA", "HILL, BRIAN R", "CAMPBELL, RHIANNA B")

all_reg_prep_ohrd <- ohrd_registration %>%
  mutate(
    COURSE_NAME = "IT Professionals Conference 2026",
    Attended = if_else(Name %in% live_absences, 0, 1),
    NETID = sub("@.*", "", Email),
    PVI = NA,
    YEAR = "2026",
    `Dupplicate?` = 'No',
    `Ticket Type` = if_else(Email %in% in_kind$Email, "Special", "General")
  ) %>%
  select(COURSE_NAME, Attended, NETID, PVI, YEAR, `Dupplicate?`, `Ticket Type`)

reg_2017_to_2026 <- bind_rows(reg_2017_to_2025, all_reg_prep_zoom, all_reg_prep_ohrd)

```


```{r fig.height = 6, include = FALSE}

yearly_turnout <- reg_2017_to_2026 %>%
  group_by(YEAR, Attended) %>%
  summarise(count = n()) %>%
  group_by(YEAR) %>%
  summarise(
    total = sum(count),
    attended = sum(count[Attended == 1]),
    turnout_rate = paste0(round(100 * attended / total, 1), "%")
  ) %>%
  mutate(YEAR = factor(YEAR, levels = sort(unique(reg_2017_to_2026$YEAR)))) %>%
  mutate(
    turnout_rate = if_else(turnout_rate == "100%", NA_character_, turnout_rate)
  )

```

```{r}

suppressWarnings(
  print(

reg_2017_to_2026 %>%
  group_by(YEAR, Attended) %>%
  summarise(.groups = "drop",  # drop the grouping to suppress the message
            count = n()) %>%

ggplot(aes(x=YEAR, y=count, fill=factor(Attended))) +
  geom_bar(stat="identity", position = "stack") + 
  scale_fill_manual(
    values = c(
      "0" = "#0479A8",
      "1" = "#9B0000"
    ),
    labels = c(
      "0" = "Absent", "1" = "Attended"
    )
  ) +
  geom_text(
    data = yearly_turnout,
    aes(x = factor(YEAR), y = total, label = turnout_rate),
    vjust = -0.5,
    inherit.aes = FALSE
  ) +
  labs(fill = "Attendance Status") +
  xlab("Conference Year") +
  ylab("Registration Tallys") +
  ggtitle("Annual Registration Trend")

))
  

```

This year we had about 18 in-person absences, and 30 Virtual registrants that did not join any sessions or watch later. We had a pretty good turn-out this year which is consistent with our numbers from last year.

### [Session Attendance Metrics]{.underline}

#### Total Attendance Recorded Throughout the Day:

The two following graphs here will portray attendance throughout the day of each conference day, to determine how strongly our attendance counts hold from earlier sessions to later sessions. This insight is valuable as it reveals when peak attendance times are during our conference days.

```{r}

legend_df <- data.frame(
  x = as_datetime("2026-05-29 9:00:00"),
  y = c(299, 178, 109),
  type = c("Total", "Virtual", "Hybrid")
)

legend_df$type <- factor(legend_df$type, levels = c("Total", "Virtual", "Hybrid"))

suppressWarnings(
  
day_one_attendance <- session_summary %>%
  mutate(
    Virtual_Attendees = as.numeric(Virtual_Attendees), 
    `In-Person_Attendees` = as.numeric(`In-Person_Attendees`)
  ) %>%
  mutate (
    Virtual_Attendees = replace_na(Virtual_Attendees, 0),
    `In-Person_Attendees` = replace_na(`In-Person_Attendees`, 0),
    Start_time = mdy_hm(Start_time, tz = "America/Chicago")
  ) %>%
  group_by(Start_time) %>%
  summarise(
    Total_Attendees = sum(Total_Attendees), 
    Virtual_Attendees = sum(Virtual_Attendees),
    `In-Person_Attendees` = sum(`In-Person_Attendees`)
  ) %>%
  filter(as.Date(Start_time) == as.Date("2026-05-28"))

)
  
  ggplot(day_one_attendance, aes(x = Start_time)) +
  geom_point(aes(y=Total_Attendees), color = "#333333") +
  geom_point(aes(y=Virtual_Attendees), color = "#0479A8") +
  geom_point(aes(y=`In-Person_Attendees`), color = "#9B0000") +
  geom_line(aes(y=Total_Attendees), color = "#333333", linewidth = 1) +
  geom_line(aes(y=Virtual_Attendees), color = "#0479A8", linewidth = 1) +
  geom_line(aes(y=`In-Person_Attendees`), color = "#9B0000", linewidth = 1) +
  ylim(0, 345) +
  coord_cartesian(xlim = range(day_one_attendance$Start_time)) +
  scale_x_datetime(breaks = unique(day_one_attendance$Start_time), date_labels = "%H:%M") +
  geom_point(
    data = legend_df,
    aes(x = x, y = y, color = type),
    size = 0, show.legend = TRUE
  ) +
  scale_color_manual(
    name = "Attendance Type",
    values = c("Total" = "#333333", "Virtual" = "#0479A8", "Hybrid" = "#9B0000")
  ) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  xlab("Session Times") +
  ylab("Attendance") +
  ggtitle("Conference Attendance: Day One")


```

```{r}
suppressWarnings(
  
day_two_attendance <- session_summary %>%
  mutate(
    Start_time = mdy_hm(Start_time, tz = "America/Chicago")
  ) %>%
  group_by(Start_time) %>%
  summarise(
    Total_Attendees = sum(Total_Attendees)
  ) %>%
  filter(as.Date(Start_time) == as.Date("2026-05-29"))

)

ggplot(day_two_attendance, aes(x=Start_time)) +
  geom_point(aes(y=Total_Attendees), color = "#333333") +
  geom_line(aes(y=Total_Attendees), linewidth = 1) +
  ylim(0, 220) +
  scale_x_datetime(breaks = unique(day_two_attendance$Start_time), date_labels = "%H:%M") +
  xlab("Session Times") +
  ylab("Attendance") +
  ggtitle("Conference Attendance: Day Two")
  
  


```

What's notable in this section is that we see just over 300 live participants at our max despite having 469 engaged participants. This shows that we are definitely seeing some virtual individuals that attend only one or two sessions, or watch recordings later. Live participation is not indicative of our overall engagement. Continuing to maintain virtual options really helps individuals be able to participate and enjoy our sessions.

#### Breakdown of Total Attendance Throughout the Day by Session:

```{r}
suppressWarnings(

session_summary %>%
  mutate(Virtual_Attendees = as.numeric(Virtual_Attendees), `In-Person_Attendees` = as.numeric(`In-Person_Attendees`))%>%
  mutate(Virtual_Attendees = replace_na(Virtual_Attendees, 0), `In-Person_Attendees` = replace_na(`In-Person_Attendees`, 0),) %>%
  arrange(desc(Total_Attendees), Start_time) %>%
  select(Session_name, Total_Attendees, Virtual_Attendees, `In-Person_Attendees`) %>%
  rename(`Session Title` = Session_name, `Total Attended` = Total_Attendees, `Attended Virtual` = Virtual_Attendees, `Attended In-Person` = `In-Person_Attendees`) %>%
  kable()

)

```

#### Observations:

The first key observation in the session attendance are our top 5 attended sessions. They keynote had the highest turnout, as it is likely that many were interested in our main event. The IT Recognition Awards was the second most attended session, many likely enjoy seeing the work of our most valued professionals.Our third place goes to "AI Agents for IT Productivity", fourth to "Building Trust in IT: Competency, Sincerity, and Care, Made Practical", and fifth to "Raised on Anime, Working in IT: How Japanese Anime Inspired Careers in IT and Cybersecurity".

One interesting note here is that our top three sessions follow with what we saw last year. Our first most attended session last year was the Keynote, the second was the IT Awards, and the third was an AI centered session. It was also interesting to see that people were really interested in the Anime session, as that was a rather unique session that interested a lot of individuals. More niche sessions should be included in our conference to shake up the typical project reporting and service oriented presentations.

Another observation made in this data is the decline of participation as the conference carries through the day. It is likely that some people attend only to see our keynote presentations and a few sessions after and return to work the rest of the afternoon.

A final observation here with the session attendance data is that networking and the unconference had pretty low attendance. 

___

### [Financial Reporting]{.underline}

This section shows high level budget information available in our 2026 Budgeting Sheet.

#### Funds Available for the 2025 IT Professionals Conference:

```{r}
financials <- data.frame(
  `Budget_Allocation` = "$12,000", 
  `Registration_Revenue` = "$6,500", 
  `Total_Budget` = "$18,500"
)

kable(as.data.frame(financials))
```

#### Funds Used for the 2025 IT Professionals Conference:

```{r}
obligations <- data.frame(
  Facility_Cost = "$700.00",
  Catering_Cost = "$6,908.00",
  Keynote_Speaker_Fee = "$0.00",
  Printing = "$1,254.99",
  Captioning = "$0.00",
  Advertising = "$300.00",
  Total = "$9,162.99"
)

kable(obligations)

```
